Attributes-based Object Classification and Segmentation

### 2010-05-12 paper.tex
changes

Our work focuses on leveraging attributes to produce accurate segmentations.
The idea is to find image regions with salient attribute distributions.  If
these regions can be combined together to for larger regions with attribute
distributions matching some object's canonical distribution then one can
declare the combined region an accurate segmentation for that object.

\begin{figure}
\centering
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
\label{fig:trucka}
}
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
\label{fig:truckb}
}
\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image
contains a car increases.}
\label{fig:truck}
\end{figure}

In practice, however, the testing of all combinations of regions to
find objects is intractable.  We use two approximatory algorithms
operating on a segmentation hierarchy to determine salient regions.
Both are subtractive algorithms, which first predict attributes on
the entire region and then proceed by observing the effects of
removing different regions during a top-down traversal of the tree.
The benefit of using these methods are that large regions that
clearly don't contribute to attribute saliency can be pruned from
the tree early in the traversal.  This approach avoids the
combinatoric complexity of a full search and, even more, prunes many
regions from the segmentation tree before they even are searched,
bringing the computational complexity, in practice, to roughly
$O(n)$ where $n$ is the number of leaves in the segmentation tree.
The flowchart of our algorithm is shown in Figure
\ref{fig:flowchart}.

While we focus on segmentation of known objects, we anticipate an application
that takes more advantage of attributes: that of segmenting \emph{unknown}
objects from an image that exhibit salient but unrecognized attribute
distributions.  This type of application brings out some of the true power of
attributes, that of assigning semantic meaning to unknown, segmented objects.

@@

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}
[Note: this section was lifted straight from our extended abstract
and has not yet been updated to reflect what we actually did.]

@@

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.
Russell et al \cite{russell06} detect the whole object in each of
the multiple segment, by assuming that most objects get segmented
correctly at least once during the multiple segmentation. Our approach
will be far less aggressive in that we will use object classes and
features (attributes in our case) that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach is very similar to this in spirit.
While our initial estimate of segmentation is from the bottom-up (while
theirs is from the top-down) we will use the hierarchical information
from the segmentation to boost confidences of segmentation at the lowest
level, similar to what they do.

Another interesting work is that of Gould et al \cite{gould08}.  They use
superpixels for an initial segmentation, build a CRF that includes a
relative location feature in the energy function and minimizes the CRF
for a final segmentation.  The relative location feature is determined
using prior location probability maps.  Our approach is similar to this
as well, in that we will also incorporate relative location information,
although ours will use attributes' relative locations rather than object
classes.  We will also use a CRF for the final segmentation, but will
use a min-cut solution since our labels are binary.
Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
adding a latent shape parameter to the CRF.  This seems like it would be
a useful addition to our system but make the scope too large.

@@

We use similar algorithm as \cite{farhadi09} to train the attribute models. Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}. Those features can capture different properties. We use kmeans to quantize all the features. The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively. All the quantized features are concatenated to form the 1384 deminsional feature.

For training, we use SVM classifier with Gaussian kernel to train
model for each attribute.

@@

We use the segmentation approach of \cite{arbelaez09}.  This
produces a hierarchical segmentation by first detecting contours
using the \emph{gPb} detector \cite{maire08}.  Once the contours are
detected, regions are discovered using a watershed algorithm after
which an Ultrametric Contour Map (UCM) is constructed, which defines
the region hierarchy.  The UCM is stored as a grayscale image with
contours around the segmented regions.  These contours have intensities
representative of the region's location in the hierarchy.  So to find
the first branch in the tree, threshold the UCM image with a value
$t$ where $t = max{I(x,y)}$ where $I(x,y)$ is the intensity at pixel
location $(x,y)$.  The thresholded image can then be flood-filled into
regions.  These regions correspond to the branches on either side of
the root node in the segmentation tree.  The next level of the tree is
found by thresholding the UCM at the next highest intensity and so on.
Figure \ref{fig:ucm} shows an example UCM image and figure \ref{fig:tree}
shows the hierarchy generated from that UCM.

@@

Our objective is to detect objects and segment them out. In our
segmentation tree, the problem changes to how to select
those nodes belong to the desired object. We estimate the
probability that a node is belong to object based on the attribute
confidence distribution. For each object, we manually give the
desired attribute distribution by common knowledge. We use the
histogram intersection between the desired distribution and the
estimated confidence distribution in each node as the similarity
measure. The histogram intersection is calculated as follows:

@@

To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm. We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
The first tree is an additive tree, where regions are subdivided into successively
smaller regions moving down in the tree.  We call it ``additive'' because the
original image can be reconstructed by adding the regions from each leaf node
together.  The figures show the nodes of the trees as containing images, but in
truth the trees contain binary masks which, when applied to the original image,
produce the shown node contents.

The second tree is ``subtractive.''  The tree has identical structure to the additive
tree and each node contains the inverse of the mask of the corresponding node
in the additive tree.

The final segmentation is obtained by pruning the region tree until a final segmentation
meeting some criterion of absolute or relative attribute saliency is found.
We have two methods for pruning the tree, each showing relative strengths and
weakness.  The first is a semi-greedy additive approach which uses the additive
tree.  The second is a greedy subtractive approach.  We now discuss each of these
in detail.

@@

In this section, we evaluate our attribute based object detection
and segmentation algorithm. We will answer four questions. (1) What
is the performance of object detection and segmentation? (2) What is
the influences of different parameters? (3) What are the advantages
of the two pruning algorithms? (4) Is vertical confidence
propagation useful? (In this draft, we only have partial results, so
not all the questions are considered.)

%\subsection{Dataset}
%\label{ssec:dataset}

We use the Pascal2008 dataset. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. We plan to do
three classes classification and segmentation, including car,
aeroplane and horse. Now we only got the results on car. We will
incorporate the other classes in the final version.

Table \ref{table:aresults} shows some of the results from running
the additive algorithm on all cars in the dataset.  The recall is
the rate of correctly detecting images with cars.  The segmentation
precision is calculated with
\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
where $M_{groundtruth}$ is the groundtruth mask calculated from the
bounding boxes stored with the annotations and $M_{pred}$ is the
predicted segmentation mask.  We of course recognize that the
bounding boxes are not a good measure of segmentation truth, but
it's the best we have available.

The segmentation precision for the additive algorithm
is far better than the precision for the subtractive algorithm (which averaged
0.09).  This is because the additive algorithm only segments images for
which it has predicted presence of a car, so that any image pruned by the
algorithm already has a high car similarity score, enhancing the segmentation.
The subtractive algorithm, on the other hand, assumes presence of a car in
the image and proceeds no matter how poor the initial similarity score is.
(For the final paper we expect to have results comparing the precision
of the two algorithms based only on images segmented by both.)

Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
results of segmentations of various images by both pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Parameter & recall & prec \\
\hline 0.8,0.4,0.1  & 0.4317 & 0.2393 \\
\hline 0.8,0.4,0.15  & 0.3849 & 0.2370 \\
\hline 0.8,0.6,0.15  & 0.2720 & 0.2501 \\
\hline
\end{tabular}
\caption{Results from the additive algorithm on all car images.
Parameter contains the three threshold, $thre\_perf$, $thre\_pos$
and $thre\_neg$, recall is the object detection recall rate and prec
is the segmentation precision on all detected images.}
\label{table:aresults}
\end{table}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
Car not detected &
\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:bad_results}
\end{figure*}

>>>>

Our work focuses on leveraging attributes to produce accurate segmentations.
The idea is to find image regions with attribute distributions very similar
to some canonical distribution for an object.  We define the ``canonical distribution''
to be an attribute distribution representative of that object.  For example, the
canonical distribution for a ``car'' would have some measure of ``shininess'', some
other measure of ``window'' and so forth.  If
regions can be combined together to for larger regions with attribute
distributions matching the object's canonical distribution then one can
declare the combined region an accurate segmentation for that object.

We note that it is possible that one segmented region may contain the object and
nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
simple objects, the true region of the object is distributed among various
segmentations.  This is because all but the most trivial objects have different
sub-regions of different colors, textures, contours, etc.  Thus we must search
for a combination of these sub-regions that make up the object.

\begin{figure}
\centering
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
\label{fig:trucka}
}
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
\label{fig:truckb}
}
\caption{Segmentation by maximizing attribute similarity to a canonical
attribute distribution for a car.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image
contains a car increases.}
\label{fig:truck}
\end{figure}

In general, the testing of all combinations of regions to
find objects is intractable.  We use two approximatory algorithms
operating on a segmentation hierarchy to determine regions belonging
to a given class.
One algorithm is additive and operates by combining regions that are likely
to be part of the object.  The other is subtractive, which first predict attributes on
the entire region and then proceeds by observing the effects of
removing different regions during a top-down traversal of the tree.
The benefit of using these methods are that large regions that
clearly don't contribute to an attribute distribution similar to the
canonical can be pruned from
the tree early in the traversal.  This approach avoids the
combinatoric complexity of a full search and, even more, prunes many
regions from the segmentation tree before they even are searched,
bringing the computational complexity, in practice, to roughly
$O(n)$ where $n$ is the number of leaves in the segmentation tree.
The flowchart of our algorithm is shown in Figure
\ref{fig:flowchart}.

This work is done using attributes as the features, but the segmentation
pruning algorithms are actually feature-type agnostic and could be used
with any image feature given a scoring function applicable to that feature.

While we focus on segmentation of known objects, we anticipate an application
that takes more advantage of attributes: that of segmenting \emph{unknown}
objects from an image that exhibit stable but unrecognized attribute
distributions.  This type of application brings out some of the true power of
attributes, that of assigning semantic meaning to unknown, segmented objects.

@@

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}

@@

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.
Russell et al \cite{russell06} detect the whole object in each of
the multiple segment, by assuming that most objects get segmented
correctly at least once during the multiple segmentation. Our approach
will be far less aggressive in that we will use object classes and
features (attributes in our case) that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach doesn't use any confidence boosting based
on the hierarchy like they do, but rather, the hierarchy is used to guide
efficient removal and combination of regions.

%Another interesting work is that of Gould et al \cite{gould08}.  They use
%superpixels for an initial segmentation, build a CRF that includes a
%relative location feature in the energy function and minimizes the CRF
%for a final segmentation.  The relative location feature is determined
%using prior location probability maps.  Our approach is similar to this
%as well, in that we will also incorporate relative location information,
%although ours will use attributes' relative locations rather than object
%classes.  We will also use a CRF for the final segmentation, but will
%use a min-cut solution since our labels are binary.
%Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
%adding a latent shape parameter to the CRF.  This seems like it would be
%a useful addition to our system but make the scope too large.

%\begin{figure}
%\centering
%\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
%\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
%\end{figure}

@@

We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models. Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.  We use kmeans to quantize the features. The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively. All quantized features are concatenated to form a 1384 dimensional feature.  These low-level features are generated for training and testing datasets using the entire image.  This is done to avoid introducing any feature artifacts as a result of black space surrounding segmented regions.

For training, we use an SVM classifier with a Gaussian kernel to train
the model for each attribute.

@@

We use the segmentation approach of \cite{arbelaez09}.  This
produces a hierarchical segmentation by first detecting contours
using the \emph{gPb} detector \cite{maire08}.  This contour detector
is advantageous because it uses brightness, color and texture
gradients at multiple scales.  Once the contours are
detected, regions are discovered using a watershed algorithm after
which an Ultrametric Contour Map (UCM) is constructed, which defines
the region hierarchy.  The UCM is stored as a grayscale image with
contours around the segmented regions.  These contours have intensities
representative of the region's location in the hierarchy.  So to find
the first branch in the tree, threshold the UCM image with a value
$t$ where $t = max{I(x,y)}$ where $I(x,y)$ is the intensity at pixel
location $(x,y)$.  The thresholded image can then be flood-filled into
regions.  These regions correspond to the branches on either side of
the root node in the segmentation tree.  The next level of the tree is
found by thresholding the two new regions of the UCM at each, respective,
next highest intensity and so on.
Figure \ref{fig:ucm} shows an example UCM image and figure \ref{fig:tree}
shows the hierarchy generated from that UCM.

@@

Our objective is to detect objects and segment them out. Using a segmentation tree
we cast the problem into one of selecting nodes that belong 
to the desired object. We estimate the
probability that a node belongs to object based on the attribute
confidence distribution. For each object, we manually determine a
canonical attribute distribution.  We use the
histogram intersection between the desired distribution and the
estimated confidence distribution in each node as the similarity
measure. The histogram intersection is calculated as follows:

@@

To select the nodes, we use two different top-down pruning algorithms, 
the ``additive'' algorithm and the ``subtractive'' algorithm. 
Each of these algorithms prunes the region tree until a final segmentation
meeting some criterion of absolute or relative attribute similarity to the canonical is found.
We now discuss each algorithm in detail.

@@

In this section, we evaluate our attribute based object classification
and segmentation algorithm. We will also analyse the advantages and disadvantages of out algorithm.\\

\subsection{Dataset}
\label{ssec:dataset}

We use the Pascal2008 dataset for both training and testing. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. Three classes are used in this experiment, including car,
aeroplane and horse. We get 328 testing images, with car 150, aeroplane 103 and horse 93. Note that one image 
can contain multiple objects in multiple classes.\\

\subsection{Measure}
\label{ssec:measure}

For object classification, we use precision and recall to measure the performance. 
For segmentation, we use the ratio of intersection and union of the prediction and 
groundtruth as the measure of precision. The segmentation
precision is calculated with
\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
where $M_{groundtruth}$ is the groundtruth mask calculated from the
bounding boxes stored with the annotations and $M_{pred}$ is the
predicted segmentation mask.  We of course recognize that the
bounding boxes are not a good measure of segmentation truth, but
it's the best we have available.\\

\subsection{Classification}
\label{ssec:classification}

Table \ref{table:aresults} shows the classification results comparing the proposed method with 
the other three baseline methods. LowFea means that we use the low level feature to train and test 
the object classification directly. Att1 means that we use the attribute distribution as the feature,
but we only test it in the whole image without segmentation. Random means random prediction. Add is our
proposed algorithm with additive pruning. The proposed algorithm has the highest precision comparing 
with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
shows the ROC curve for each class and the average.\\

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Methods & Precision(\%) & Recall(\%) \\
\hline LowFea  & 55.97 & 70.96 \\
\hline Att1    & 51.89 & 51.89 \\
\hline Random  & 35.19 & 50.00 \\
\hline Add     & 60.82 & 54.06 \\
\hline
\end{tabular}
\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
\label{table:aresults}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
\caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:roc_class}
\end{figure}

\subsection{Segmentation}
\label{ssec:segmentation}

Figure \ref{fig:roc_seg} shows the segmentation precision of additive pruning 
versus the false positive rate of object classification. The segmentation precision
is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.\\

Figures \ref{fig:car_good_results} and \ref{fig:car_bad_results} show the
segmentations of car images by both additive and subtractive pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.\\

Figures \ref{fig:aeroplane_good_results}, \ref{fig:aeroplane_bad_results} and 
\ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
segmentation results of additive algorithm on aeroplane and horse classes. Because of the
high complexity of the subtractive algorithm, we did not run it on these two classes. The good 
results are accurate to segment out the objects. One important note is that our algorithm can segment out
multiple objects at the same time. The bad segmentations either miss 
part of the object or contain so much background. The bad ones are caused 
by two reasons. First, the hierarchical segmentation tree is not fine enough. We did not use all 
levels in the segmentation tree. The more levels we use, the more time we need to spend on it. 
Also when the segments are too small, the attribute detection is nearly random, because the small regions 
do not have enough points to represent their properties. Second, the training of attributes based on
bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
This is especially obvious to the horse images, since horses are not convex enough in the images. 
All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
left one which only contains grass. These images prove that the grass or trees models are actually
included in the horse model.\\

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
\caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:roc_seg}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/SubSegPrec.eps}
\caption{Graph of the precision of the subtractive segmentation
algorithm against confidence, or attribute similarity.  Despite
the noise, there is an upward trend in the precision
as the similarity score increases, as shown by the 
quadratic least-squares fit.}
\label{fig:sub_seg_prec}
\end{figure}

%\begin{figure*}[p]
%\centering
%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
%\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
%\end{tabular}
%\caption{Selected results from segmentation of cars from the Pascal2008
%dataset.  The first row shows the original image.  The second row shows
%the best segmentation from the additive algorithm.  The third row shows
%the segmentation from the subtractive algorithm with $f=0.9$.}
%\label{fig:good_results}
%\end{figure*}

%\begin{figure*}[p]
%\centering
%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
%\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
%Car not detected &
%\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
%\end{tabular}
%\caption{Selected results from segmentation of cars from the Pascal2008
%dataset.  The first row shows the original image.  The second row shows
%the best segmentation from the additive algorithm.  The third row shows
%the segmentation from the subtractive algorithm with $f=0.9$.}
%\label{fig:bad_results}
%\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:car_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_001961.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_003132.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004312.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004414.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_001961.jpg_1_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_003132.jpg_1_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004312.jpg_1_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004414.jpg_1_bad.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/sub_results/good/2008_001961_0.80.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/good/2008_003132_1.10.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/good/2008_004312_1.00.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/good/2008_004414_0.90.jpg.eps} \\

\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:car_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:aeroplane_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:aeroplane_bad_results}
\end{figure*}
